Group 1: Predicting the Outcomes of Tennis Tournaments

### 2019-12-11 Group1Prez.Rmd
Trying to get .rmd to knit
Corrected some errors More to come

---
title: "Group 1: Tennis "
author: "Olivia Beck, Emma Lewis, Ryan Volkert"
date: "December 12, 2019"
output: beamer_presentation
header-includes: 
  - \usepackage{booktabs} 
  - \usepackage{longtable} 
  - \usepackage{array} 
  - \usepackage{multirow} 
  - \usepackage{wrapfig} 
  - \usepackage{float} 
  - \usepackage{colortbl} 
  - \usepackage{pdflscape} 
  - \usepackage{tabu} 
  - \usepackage{threeparttable} 
  - \usepackage{threeparttablex} 
  - \usepackage[normalem]{ulem} 
  - \usepackage{makecell} 
  - \usepackage{xcolor}

@@

- It is noted that points in tennis are not iid for most purposes this is not a bad assumption as the divergence from iid is small

- Both two out of three and three out of five set matches were considered aloowing for 13-point tiebreaker in each set if needed

## The Game of Tennis

@@

## Game of Tennis

@@

Where, $p_A^S(i,j)$ is defined recursivly as:

@@

Where,  $p_A^T(i,j)$ is defined recursivly as:

@@

  - Men and Women semifinalists in the 2002 Wimbledon tournament

@@

  - Men and Women semifinalists in the 2019 Wibledon tournament

@@

```{r, warning=FALSE, echo=FALSE}
WimWomen <- read_csv("2019 Womens Wimbledon.csv")

@@

T1<- table(base::sample(WimWomen$Name, 2000, prob = WimWomen$`P(Winning a Rally)`, replace = TRUE))

@@

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab("Players") +
  ylab("P(Win the Tournement)")
  ggtitle("Which Player Won the Tournement?")

@@

```{r, warning=FALSE, echo=FALSE}
WimMen <- read_csv("2019 Men's Wimbledon.csv")

>>>>

---
title: "Group 1: Predicting the Outcomes of Tennis Tournaments"
subtitle: "A Monte Carlo Approach"
author: "Olivia Beck, Emma Lewis, Ryan Volkert"
date: "December 12, 2019"
output: beamer_presentation
header-includes: 
  - \usepackage{booktabs} 
  - \usepackage{longtable} 
  - \usepackage{array} 
  - \usepackage{multirow} 
  - \usepackage{wrapfig} 
  - \usepackage{float} 
  - \usepackage{colortbl} 
  - \usepackage{pdflscape} 
  - \usepackage{tabu} 
  - \usepackage{threeparttable} 
  - \usepackage{threeparttablex} 
  - \usepackage[normalem]{ulem} 
  - \usepackage{makecell} 
  - \usepackage{xcolor}

@@

- It is noted that points in tennis are not iid for most purposes
  - This is not a bad assumption as the divergence from iid is small

- Both two out of three and three out of five set matches were considered allowing for 13-point tiebreaker in each set if needed

## The Rules of Tennis

@@

## The Rules of Tennis

@@

Where, $p_A^S(i,j)$ is defined recursively as:

@@

Where,  $p_A^T(i,j)$ is defined recursively as:

@@

  - Men and Women semifinalists in the 2002 Wimbledon tournament \pause

@@

  - Men and Women semifinalists in the 2019 Wimbledon tournament

@@

```{r, warning=FALSE, echo=FALSE, message=F}
WimWomen <- read_csv("2019 Womens Wimbledon.csv")

@@

T1 <- table(base::sample(WimWomen$Name, 2000, prob = WimWomen$`P(Winning a Rally)`, replace = TRUE))

@@

ggplot(data.frame(T1)) +
  geom_col(aes(x=Var1, y=Freq/2000)) +
  xlab("Players") +
  ylab("P(Win the Tournament)") +
  ggtitle("Which Player Won the Tournament?")

@@

```{r, warning=FALSE, echo=FALSE, message=F}
WimMen <- read_csv("2019 Men's Wimbledon.csv")
